### 2020-09-25 Paper/eacl2021.tex
added stuff from overleaf

%
% File eacl2021.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{eacl2021}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Instructions for EACL 2021 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
This document contains the instructions for preparing a manuscript for the proceedings of EACL 2021.
The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
These instructions should be used for both papers submitted for review and for final versions of accepted papers.
Authors are asked to conform to all the directions reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted
by Steven Bethard, Ryan Cotterrell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for 
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Michell and Stephanie Lukin,
2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted to EACL 2021 or accepted for publication in its proceedings.
All authors are required to adhere to these specifications.
Authors are required to provide a Portable Document Format (PDF) version of their papers.
\textbf{The proceedings are designed for printing on A4 paper.}

\section{Electronically-available resources}

EACL provides this description and accompanying style files at
\begin{quote}
\url{http://eacl2021.org/downloads/eacl2021-templates.zip}
\end{quote}
We strongly recommend the use of these style files, which have been appropriately tailored for the EACL 2021 proceedings.

\paragraph{\LaTeX-specific details:}
The templates include the \LaTeX2e{} source (\texttt{\small eacl2021.tex}),
the \LaTeX2e{} style file used to format it (\texttt{\small eacl2021.sty}),
an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
an example bibliography (\texttt{\small acl2020.bib}),
and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).

\section{Length of Submission}
\label{sec:length}

The conference accepts submissions of long papers and short papers.
Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
As always, the respective call for papers is the authoritative source.

\section{Anonymity}
As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations). Furthermore, self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
We previously showed \citep{Gusfield:97} \ldots
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
\citet{Gusfield:97} previously showed\ldots
\end{quote}
Please do not use anonymous citations and do not include acknowledgements.
\textbf{Papers that do not conform to these requirements may be rejected without review.}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.

\paragraph{\LaTeX-specific details:}
For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.

\section{Multiple Submission Policy}
Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by EACL 2021. Authors of papers accepted for presentation at EACL 2021 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented. We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.

Authors submitting more than one paper to EACL 2021 must ensure that submissions do not overlap significantly ($>25\%$) with each other in content or results.

\section{Formatting Instructions}

Manuscripts must be in two-column format.
Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
\textbf{Type single-spaced.}
Start all pages directly under the top margin.
The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.

\paragraph{\LaTeX-specific details:}
The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.

\subsection{File Format}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
Please make sure that you select the option of including ALL the fonts.
\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
Such images may reproduce poorly.
In this case, try alternative ways to obtain the PDF.
One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.

\paragraph{\LaTeX-specific details:}
PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted.
The exact dimensions for a page on A4 paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.

Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.

\begin{table}
\centering
\begin{tabular}{lrl}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\caption{\label{font-table} Font guide. }
\end{table}

\paragraph{\LaTeX-specific details:}
To use Times Roman in \LaTeX2e{}, put the following in the preamble:
\begin{quote}
\small
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}

\subsection{Ruler}
A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera ready copy should not contain a ruler.

\paragraph{Reviewers:}
note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).

\paragraph{\LaTeX-specific details:}
The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.

\subsection{Title and Authors}
\label{ssec:title-authors}

Center the title, author's name(s) and affiliation(s) across both columns.
Do not use footnotes for affiliations.
Place the title centered at the top of the first page, in a 15-point bold font.
Long titles should be typed on two lines without a blank line intervening.
Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
Do not use only initials for given names (middle initials are allowed).
Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
conventionally in all capitals.
The affiliation should contain the author's complete address, and if possible, an electronic mail address.

The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.

Start the body of the first page 7.5 cm from the top of the page.
\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}

\subsection{Abstract}
Use two-column format when you begin the abstract.
Type the abstract at the beginning of the first column.
The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by 0.6 cm on each side.
Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
The abstract should be a concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.
The abstract text should be in 10 point font.

\subsection{Text}
Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.

Indent 0.4 cm when starting a new paragraph.

\subsection{Sections}

Format section and subsection headings in the style shown on the present document.
Use numbered sections (Arabic numerals) to facilitate cross references.
Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.

\subsection{Footnotes}
Put footnotes at the bottom of the page and use 9 point font.
They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}

\subsection{Graphics}

Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
Wide illustrations may run across both columns.
Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.

\paragraph{Captions:}
Provide a caption for every illustration; number each one sequentially in the form:
``Figure 1. Caption of the Figure.''
``Table 1. Caption of the Table.''
Type the captions of the figures and tables below the body, using 10 point text.
Captions should be placed below illustrations.
Captions that are one line are centered (see Table~\ref{font-table}).
Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\paragraph{\LaTeX-specific details:}
The style files are compatible with the caption and subcaption packages; do not add optional arguments.
\textbf{Do not override the default caption sizes.}

\subsection{Hyperlinks}
Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.

\subsection{Citations}
Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.

Refrain from using full citations as sentence constituents.
Instead of
\begin{quote}
  ``\citep{Gusfield:97} showed that ...''
\end{quote}
write
\begin{quote}
``\citet{Gusfield:97} showed that ...''
\end{quote}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
\hline
\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

\paragraph{\LaTeX-specific details:}
Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).

\subsection{References}
Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
Arrange the references alphabetically by first author, rather than by order of occurrence in the text.

Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
Psychological Association\/}~\citep{APA:83}.
Use full names for authors, not just initials.

Submissions should accurately reference prior and related work, including code and data.
If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
Authors should not rely on automated citation indices to provide accurate references for prior and related work.

The following text cites various types of articles so that the references section of the present document will include them.
\begin{itemize}
\item Example article in journal: \citep{Ando2005}.
\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
\item Example article in proceedings, without location: \citep{andrew2007scalable}.
\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
\end{itemize}

\paragraph{\LaTeX-specific details:}
The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{\small eacl2021.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{eacl2021}|
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the anthology and your own bib file, use the following instead of the above.
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{anthology,eacl2021}|
\end{quote}

\subsection{Digital Object Identifiers}
As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.

All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.

\paragraph{\LaTeX-specific details:}
Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.

\subsection{Appendices}
Appendices, if any, directly follow the text and the
references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
Letter them in sequence and provide an informative title:
\textbf{Appendix A. Title of Appendix}.

\section{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
A simple criterion:
All curves and points in your figures should be clearly distinguishable without color.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in the order of:
\begin{center}
\begin{tabular}{c}
original-form \\
transliteration \\
``translation''
\end{tabular}
\end{center}

\section{\LaTeX{} Compilation Issues}
You may encounter the following error during compilation: 
\begin{quote}
{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
\end{quote}
This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
To fix this, the style file contains a patch consisting of two lines:
(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small eacl2021.sty}), and
(2) A long line below (line 456 in \texttt{\small eacl2021.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:

\noindent
{\small\verb|\usepackage[nohyperref]{eacl2021}|}

\noindent
Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})

\section*{Acknowledgments}

The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
Do not include this section when submitting your paper for review.

\bibliography{anthology,eacl2021}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
\textbf{Submissions that misuse the supplementary material may be rejected without review.}
Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
(Source code and data should be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.

\end{document}

### 2020-09-25 Paper/main.tex
added files for main doc
added separate intro tex file for sample

--- 2020-09-25 Paper/eacl2021.tex
@@
 
-\title{Instructions for EACL 2021 Proceedings}
+\title{Paper Title}
 
@@
 \maketitle
+
 \begin{abstract}
-This document contains the instructions for preparing a manuscript for the proceedings of EACL 2021.
-The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-These instructions should be used for both papers submitted for review and for final versions of accepted papers.
-Authors are asked to conform to all the directions reported in this document.
+    \input{abstract.tex}
 \end{abstract}
@@
 
-This document has been adapted
-by Steven Bethard, Ryan Cotterrell and Rui Yan
-from the instructions for earlier ACL and NAACL proceedings, including those for 
-ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
-NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
-ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
-NAACL 2018 by Margaret Michell and Stephanie Lukin,
-2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan, 
-NAACL 2017 by Margaret Mitchell, 
-ACL 2012 by Maggie Li and Michael White, 
-ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
-ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
-ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
-ACL 2002 by Eugene Charniak and Dekang Lin, 
-and earlier ACL and EACL formats written by several people, including
-John Chen, Henry S. Thompson and Donald Walker.
-Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.
+\section{Introduction}
+\input{intro.tex}
+\label{sec:intro}
 
-\section{Introduction}
-
-The following instructions are directed to authors of papers submitted to EACL 2021 or accepted for publication in its proceedings.
-All authors are required to adhere to these specifications.
-Authors are required to provide a Portable Document Format (PDF) version of their papers.
-\textbf{The proceedings are designed for printing on A4 paper.}
-
-\section{Electronically-available resources}
-
-EACL provides this description and accompanying style files at
-\begin{quote}
-\url{http://eacl2021.org/downloads/eacl2021-templates.zip}
-\end{quote}
-We strongly recommend the use of these style files, which have been appropriately tailored for the EACL 2021 proceedings.
-
-\paragraph{\LaTeX-specific details:}
-The templates include the \LaTeX2e{} source (\texttt{\small eacl2021.tex}),
-the \LaTeX2e{} style file used to format it (\texttt{\small eacl2021.sty}),
-an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
-an example bibliography (\texttt{\small acl2020.bib}),
-and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).
-
-\section{Length of Submission}
-\label{sec:length}
-
-The conference accepts submissions of long papers and short papers.
-Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
-Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
-Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
-Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
-For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
-Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
-
-The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
-There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
-Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
-The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
-Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
-Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.
-
-Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
-As always, the respective call for papers is the authoritative source.
-
-\section{Anonymity}
-As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations).
-Furthermore, self-references that reveal the author's identity, \emph{e.g.},
-\begin{quote}
-We previously showed \citep{Gusfield:97} \ldots
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-\citet{Gusfield:97} previously showed\ldots
-\end{quote}
-Please do not use anonymous citations and do not include acknowledgements.
-\textbf{Papers that do not conform to these requirements may be rejected without review.}
-
-Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
-Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.
-
-Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.
-
-\paragraph{\LaTeX-specific details:}
-For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
-For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.
-
-\section{Multiple Submission Policy}
-Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by EACL 2021.
-Authors of papers accepted for presentation at EACL 2021 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented.
-We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.
-
-Authors submitting more than one paper to EACL 2021 must ensure that submissions do not overlap significantly ($>25\%$) with each other in content or results.
-
-\section{Formatting Instructions}
-
-Manuscripts must be in two-column format.
-Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
-\textbf{Type single-spaced.}
-Start all pages directly under the top margin.
-The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.
-
-\paragraph{\LaTeX-specific details:}
-The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.
-
-\subsection{File Format}
-\label{sect:pdf}
-
-For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
-Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
-When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
-Please make sure that you select the option of including ALL the fonts.
-\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
-Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
-Such images may reproduce poorly.
-In this case, try alternative ways to obtain the PDF.
-One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.
-
-It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
-Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.
-
-\paragraph{\LaTeX-specific details:}
-PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
-If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
-To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
-in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.
-
-\subsection{Layout}
-\label{ssec:layout}
-
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted.
-The exact dimensions for a page on A4 paper are:
-
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
-If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.
-
-Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.
-
-\begin{table}
-\centering
-\begin{tabular}{lrl}
-\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-subsection titles & 11 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\caption{\label{font-table} Font guide. }
-\end{table}
-
-\paragraph{\LaTeX-specific details:}
-To use Times Roman in \LaTeX2e{}, put the following in the preamble:
-\begin{quote}
-\small
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-
-\subsection{Ruler}
-A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera ready copy should not contain a ruler.
-
-\paragraph{Reviewers:}
-note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).
-
-\paragraph{\LaTeX-specific details:}
-The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.
-
-\subsection{Title and Authors}
-\label{ssec:title-authors}
-
-Center the title, author's name(s) and affiliation(s) across both columns.
-Do not use footnotes for affiliations.
-Place the title centered at the top of the first page, in a 15-point bold font.
-Long titles should be typed on two lines without a blank line intervening.
-Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
-Do not use only initials for given names (middle initials are allowed).
-Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
-Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.
-The affiliation should contain the author's complete address, and if possible, an electronic mail address.
-
-The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
-If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.
-
-Start the body of the first page 7.5 cm from the top of the page.
-\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}
-
-\subsection{Abstract}
-Use two-column format when you begin the abstract.
-Type the abstract at the beginning of the first column.
-The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by 0.6 cm on each side.
-Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
-The abstract should be a concise summary of the general thesis and conclusions of the paper.
-It should be no longer than 200 words.
-The abstract text should be in 10 point font.
-
-\subsection{Text}
-Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.
-
-Indent 0.4 cm when starting a new paragraph.
-
-\subsection{Sections}
-
-Format section and subsection headings in the style shown on the present document.
-Use numbered sections (Arabic numerals) to facilitate cross references.
-Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.
-
-\subsection{Footnotes}
-Put footnotes at the bottom of the page and use 9 point font.
-They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
-Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
-Wide illustrations may run across both columns.
-Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.
-
-\paragraph{Captions:}
-Provide a caption for every illustration; number each one sequentially in the form:
-``Figure 1. Caption of the Figure.''
-``Table 1. Caption of the Table.''
-Type the captions of the figures and tables below the body, using 10 point text.
-Captions should be placed below illustrations.
-Captions that are one line are centered (see Table~\ref{font-table}).
-Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).
-
-\begin{table}
-\centering
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular}
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\
-\hline
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
-
-\paragraph{\LaTeX-specific details:}
-The style files are compatible with the caption and subcaption packages; do not add optional arguments.
-\textbf{Do not override the default caption sizes.}
-
-\subsection{Hyperlinks}
-Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.
-
-\subsection{Citations}
-Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
-Append lowercase letters to the year in cases of ambiguities.  
-Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.
-
-Refrain from using full citations as sentence constituents.
-Instead of
-\begin{quote}
-  ``\citep{Gusfield:97} showed that ...''
-\end{quote}
-write
-\begin{quote}
-``\citet{Gusfield:97} showed that ...''
-\end{quote}
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-\hline
-\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
-\hline
-\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
-\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
-\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
-\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
-\hline
-\end{tabular}
-\caption{\label{citation-guide}
-Citation commands supported by the style file.
-The style is based on the natbib package and supports all natbib citation commands.
-It also supports commands defined in previous ACL style files for compatibility.
-}
-\end{table*}
-
-\paragraph{\LaTeX-specific details:}
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
-You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
-You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).
-
-\subsection{References}
-Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
-Arrange the references alphabetically by first author, rather than by order of occurrence in the text.
-
-Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
-Psychological Association\/}~\citep{APA:83}.
-Use full names for authors, not just initials.
-
-Submissions should accurately reference prior and related work, including code and data.
-If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
-If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
-Authors should not rely on automated citation indices to provide accurate references for prior and related work.
-
-The following text cites various types of articles so that the references section of the present document will include them.
-\begin{itemize}
-\item Example article in journal: \citep{Ando2005}.
-\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
-\item Example article in proceedings, without location: \citep{andrew2007scalable}.
-\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
-\end{itemize}
-
-\paragraph{\LaTeX-specific details:}
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{\small eacl2021.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{eacl2021}|
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the anthology and your own bib file, use the following instead of the above.
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{anthology,eacl2021}|
-\end{quote}
-
-\subsection{Digital Object Identifiers}
-As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.
-
-All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
-Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
-As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
-We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.
-
-\paragraph{\LaTeX-specific details:}
-Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
-If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.
-
-\subsection{Appendices}
-Appendices, if any, directly follow the text and the
-references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
-Letter them in sequence and provide an informative title:
-\textbf{Appendix A. Title of Appendix}.
-
-\section{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
-Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
-A simple criterion:
-All curves and points in your figures should be clearly distinguishable without color.
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in the order of:
-\begin{center}
-\begin{tabular}{c}
-original-form \\
-transliteration \\
-``translation''
-\end{tabular}
-\end{center}
-
-\section{\LaTeX{} Compilation Issues}
-You may encounter the following error during compilation: 
-\begin{quote}
-{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
-\end{quote}
-This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
-To fix this, the style file contains a patch consisting of two lines:
-(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small eacl2021.sty}), and
-(2) A long line below (line 456 in \texttt{\small eacl2021.sty}).
-
-If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:
-
-\noindent
-{\small\verb|\usepackage[nohyperref]{eacl2021}|}
-
-\noindent
-Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
-Do not include this section when submitting your paper for review.
-
+\newpage
+\balance
+%%%%%%%%%%%
+{
     \bibliography{anthology,eacl2021}
     \bibliographystyle{acl_natbib}
+} 
+%%%%%%%%%%%
 
 \appendix
-
 \section{Appendices}
 \label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
 
@@
 \label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
-Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
-\textbf{Submissions that misuse the supplementary material may be rejected without review.}
-Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
-(Source code and data should be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.
 

### 2020-09-29 Paper/investigating-effectiveness.tex
added file for paper summary - wip

Active learning only selects the most informative instances from an unlabelled dataset
to expedite the learning process, making it effective in cases where unlabelled data is 
plentiful. Recent work has shown that representations of natural languages based on 
learned word embeddings can be useful for a wide range of NLP tasks, where 
transformer-based pre-trained models such as BERT (Bi-directional encoder representations 
from transformers), that are pre-trained with large-scale generic corpora and finetuned 
for specific tasks, have shown impressive results. However, there is little work devoted to 
leveraging word embeddings and transformer-based language models, though they are widely 
applied in text classification.

### 2020-09-29 Paper/investigating-effectiveness.tex
investigating-effectiveness... paper work in progress
added more on related work

@@
 leveraging word embeddings and transformer-based language models, though they are widely 
-applied in text classification.
+applied in text classification. \cite{lu2020investigating} addresses four primary research 
+questions: 
+\begin{enumerate}
+    \item Are representations generated from pre-trained transformer language models more 
+        effective than others with regards to active learning for text labelling?
+    \item Is it required to use standard large models, or can lightweight models be used to 
+        reduce the computational burden for active learning? Are there performance drops?
+    \item Is it more effective to represent a document using aggregate of word embeddings 
+        produced by the model or the CLS token? 
+    \item Can the performance of the active learning system be improveed by using a 
+        transformer-based model by fine-tuning? 
+\end{enumerate}
+
+\cite{lu2020investigating} uses an evaluation based on 8 datasets from different domains
+to show that transformer-based language models consistently outperform more commonly used 
+vector representations like word embeddings or bag-of-words.

### 2020-10-01 Paper/active-learning-interactive.tex
added active-learning-interactive tex file

Recent work in machine translation approaches has focused on integrating active learning
with interaction-based neural machine translation. These modifications have been experimentally 
employed with unbounded real-time streaming data \cite{peris2020active} with the objective of selecting 
only those sentences which are very difficult for the translation system to accurately classify upon 
during the initial stages. Results have shown promise in improving the overall quality of translation 
and reducing human intervention in the process. A core component of this approach involves tweaking the 
sampling strategies involved to maximize the probability of selecting only the most “difficult” sentences. 
However, these results have a lack of representation and probable efficacy with respect to low-resource-based 
multilingual paradigms. The effectiveness of slight alterations in the overall encoder-decoder transformer 
network also needs to be experimented upon to possibly generate higher quality translations.

### 2020-10-10 Paper/investigating-effectiveness.tex
added FCE Parser

@@
 to show that transformer-based language models consistently outperform more commonly used 
-vector representations like word embeddings or bag-of-words.
+vector representations like word embeddings or bag-of-words. Comparing to BERT-like models, 
+representations based on Roberta produce the best results. Additionally, averaged word 
+representations are the most effective as compared to CLS tokens. An Adaptive Tuning 
+Active Learning (ATAL) algorithm is proposed where labelled information is utilized for 
+improving effectiveness of embeddings other than training classifiers.

### 2020-10-10 Scripts/FCE_Parser/generate_vocab.py

@@ -1,0 +1,112 @@
+#! /usr/bin/env python
+# Copyright 2017 Google Inc.
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#      http://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+#
+# Source: https://github.com/google/seq2seq/blob/master/bin/tools/generate_vocab.py
+# Changes made:
+#   Saves vocabulary in file
+#
+
+#pylint: disable=invalid-name
+"""
+Generate vocabulary for a tokenized text file.
+"""
+
+import sys
+import argparse
+import collections
+import logging
+
+parser = argparse.ArgumentParser(
+    description="Generate vocabulary for a tokenized text file.")
+parser.add_argument(
+    "--min_frequency",
+    dest="min_frequency",
+    type=int,
+    default=0,
+    help="Minimum frequency of a word to be included in the vocabulary.")
+parser.add_argument(
+    "--max_vocab_size",
+    dest="max_vocab_size",
+    type=int,
+    help="Maximum number of tokens in the vocabulary")
+parser.add_argument(
+    "--downcase",
+    dest="downcase",
+    type=bool,
+    help="If set to true, downcase all text before processing.",
+    default=False)
+parser.add_argument(
+    "--infile",
+    nargs="?",
+    type=argparse.FileType("r"),
+    default=sys.stdin,
+    help="Input tokenized text file to be processed.")
+parser.add_argument(
+    "--delimiter",
+    dest="delimiter",
+    type=str,
+    default=" ",
+    help="Delimiter character for tokenizing. Use \" \" and \"\" for word and char level respectively."
+)
+parser.add_argument(
+    "--outfile",
+    dest="outfile",
+    type=str,
+    default="vocab.txt",
+    help="Name of file to save vocab."
+)
+args = parser.parse_args()
+
+# Counter for all tokens in the vocabulary
+cnt = collections.Counter()
+
+for line in args.infile:
+  if args.downcase:
[…]

### 2020-10-10 Scripts/FCE_Parser/main_xml_to_txt.py

@@ -1,0 +1,26 @@
+
+import argparse
+import utils
+from FCECorpusHandler import FCECorpusHandler
+
+
+""" Module to parse XML in Python using minidom
+"""
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='Extracts transcript and summary from FCE Corpus.')
+    parser.add_argument('--fce_xml_dir', type=str, default=utils.project_dir_name() + '/data/',
+                        help='FCE Corpus download directory')
+    parser.add_argument('--results_dir', type=str,
+                        default=utils.project_dir_name() + '/data/fce_txt/',
+                        help='FCE Corpus txt format')
+    args = parser.parse_args()
+
+    fceCorpusHandler = FCECorpusHandler(args)
+
+    fceCorpusHandler.get_train_dev_test_sets()
+
+    fceCorpusHandler.xml_to_txt(data_type="train")
+    fceCorpusHandler.xml_to_txt(data_type="dev")
+    fceCorpusHandler.xml_to_txt(data_type="test")

### 2020-10-10 Paper/active-learning-interactive.tex
changes in sections

@@
-Recent work in machine translation approaches has focused on integrating active learning
-with interaction-based neural machine translation. These modifications have been experimentally 
-employed with unbounded real-time streaming data \cite{peris2020active} with the objective of selecting 
-only those sentences which are very difficult for the translation system to accurately classify upon 
-during the initial stages. Results have shown promise in improving the overall quality of translation 
-and reducing human intervention in the process. A core component of this approach involves tweaking the 
-sampling strategies involved to maximize the probability of selecting only the most “difficult” sentences. 
-However, these results have a lack of representation and probable efficacy with respect to low-resource-based 
-multilingual paradigms. The effectiveness of slight alterations in the overall encoder-decoder transformer 
-network also needs to be experimented upon to possibly generate higher quality translations.
+\subsection{Active learning for interactive neural machine translation of data streams}
+\label{active-learning-interactive}
+
+A series of recent research works discuss and introduce a variety of model- and data-based methods to select the most informative samples to improve an NMT's performance.
+\citet{zhang2018active} propose two active learning techniques for sentence selection, based on semantic similarity between the sentence embeddings and decoder probability as a token of translation quality, while \citet{peris2020active} explore the application of active learning methods in the interactive translation of large data streams.
+The latter work uses the attention mechanism of a neural machine translation system to select only those sentences worthy of human annotation for translation.
+In a more recent approach, \citet{zeng2019empirical} perform an empirical evaluation of different AL methods for Transformers \cite{vaswani2017attention}, analyzing data-driven approaches, that sample instances based only on two sets of labeled and unlabeled sentences, and model-driven methods, which additionally incorporate information from the current model into sampling.
+However their work notes the weak performance of Coverage Sampling compared to the other techniques, due to the complex nature of the state-of-the art multi-layer multi-head Natural Language Processing architectures, a phenomenon we are addressing with the current work.
+A series of works explored the shortcomings of Active Learning approaches in Machine Translation.
+\cite{lowell2018practical} observe the performance drop issues arising in applying Active Learning across different models and tasks and discuss the methods' generalization constraints.
+Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a neural machine translation system in learning sentence semantic representations, concluding on a non-significant difference with a random sentence selection approach.

### 2020-10-10 Paper/error-classification.tex
changes in sections

\subsection{Error Classification in Machine Translation}
\label{ssec:related_errors}

There exists a significant body of work in the area of error classification of text for machine translation, and proposed methods can be primarily divided into manual or automatic. In the former category, approaches focus on describing detailed error typologies to be used in conducting a systematic manual error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}. On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output of a MT system and its reference translation. Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error automatic classification \citet{popovic2019automatic}. In the most recent approaches, error detection is examined as an application of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}, and currently serve as the state of the art machine learning methods, utilizing powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, overcoming the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

### 2020-10-10 Scripts/FCE_Parser/FCECorpusHandler.py
added more stuff

@@ -57,7 +57,8 @@ class FCECorpusHandler:
             # Delete .tar.gz file
             os.remove(targz_fce_filename)
         else:
-            print("FCE Error Detection Corpus has already been downloaded in: {}".format(self.fce_error_detection_dir))
+            print("FCE Error Detection Corpus has already been downloaded in: {}".format(
+                self.fce_error_detection_dir))
 
     def download_fce_corpus(self):
         """ Check if FCE Corpus exists and only download it if it doesn't
@@ -96,7 +97,8 @@ class FCECorpusHandler:
 
         # Separate train, dev, test
         train_dev_test_path = self.fce_error_detection_dir + '/filenames/'
-        train_dev_test_files = [f for f in os.listdir(train_dev_test_path) if f.endswith('.txt')]
+        train_dev_test_files = [f for f in os.listdir(
+            train_dev_test_path) if f.endswith('.txt')]
         print(train_dev_test_files)
         for file in train_dev_test_files:
             set_dir = self.fce_dir + '/' + file.split('.')[1] + '/'
@@ -112,7 +114,8 @@ class FCECorpusHandler:
     def xml_to_txt(self, data_type='train', verbose=False):
         print("\nGet train-dev-test sets")
         fce_dir_dataset = '{}/{}/'.format(self.fce_dir, data_type)
-        train_dev_test_files = [f for f in os.listdir(fce_dir_dataset) if f.endswith('.xml')]
+        train_dev_test_files = [f for f in os.listdir(
+            fce_dir_dataset) if f.endswith('.xml')]
 
         # Convert from xml to txt
         incorrect_sentences = []
@@ -124,7 +127,8 @@ class FCECorpusHandler:
             mydoc = minidom.parse(fce_dir_dataset + f)
             items_essay = mydoc.getElementsByTagName('p')
             for item_essay in items_essay:
-                incorrect_sent, correct_sent = self.strip_str(item_essay, verbose=verbose)
+                incorrect_sent, correct_sent = self.strip_str(
+                    item_essay, verbose=verbose)
                 incorrect_sentences.append(incorrect_sent)
                 correct_sentences.append(correct_sent)
 
@@ -147,6 +151,7 @@ class FCECorpusHandler:
     def strip_str(self, item_essay, verbose=False):
         incorrect_sent = ''
         correct_sent = ''
+        error_tags = ''
         for child in item_essay.childNodes:
             if child.localName is None:  # no child nodes
                 segment = child.data
[…]

### 2020-10-10 Scripts/FCE_Parser/main_xml_to_txt.py

@@ -21,6 +21,8 @@ if __name__ == '__main__':
 
     fceCorpusHandler.get_train_dev_test_sets()
 
-    fceCorpusHandler.xml_to_txt(data_type="train")
-    fceCorpusHandler.xml_to_txt(data_type="dev")
-    fceCorpusHandler.xml_to_txt(data_type="test")
+    # fceCorpusHandler.xml_to_txt(data_type="train")
+    # fceCorpusHandler.xml_to_txt(data_type="dev")
+    # fceCorpusHandler.xml_to_txt(data_type="test")
+    
+    fceCorpusHandler.parse_data()

### 2020-10-10 Paper/error-classification.tex
added more stuff
minor changes

@@
-\subsection{Error Classification in Machine Translation}
-\label{ssec:related_errors}
-
 There exists a significant body of work in the area of error classification of text for machine translation, and proposed methods can be primarily divided into manual or automatic.
@@
 On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output of a MT system and its reference translation.
-Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error automatic classification \citet{popovic2019automatic}.
+Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error automatic classification \cite{popovic2019automatic}.
+
 In the most recent approaches, error detection is examined as an application of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}, and currently serve as the state of the art machine learning methods, utilizing powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, overcoming the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/error-classification.tex
small update

@@
-There exists a significant body of work in the area of error classification of text for machine translation, and proposed methods can be primarily divided into manual or automatic.
-In the former category, approaches focus on describing detailed error typologies to be used in conducting a systematic manual error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}.
-On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output of a MT system and its reference translation.
-Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error automatic classification \cite{popovic2019automatic}.
-
-In the most recent approaches, error detection is examined as an application of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}, and currently serve as the state of the art machine learning methods, utilizing powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, overcoming the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.
+There exists a significant body of work in the area of error classification of text for machine translation, 
+and proposed methods can be primarily divided into manual or automatic. In the former category, approaches focus 
+on describing detailed error typologies to be used in conducting a systematic manual error annotation 
+\cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}. 
+On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} 
+detect predefined error types, by measuring the alignment of the output of a MT system and its reference translation. 
+Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories
+ \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error 
+ automatic classification \cite{popovic2019automatic}. In the most recent approaches, error detection is examined as 
+ an application of neural sequence labeling methods, which aim to detect errors and predict their surrounding context 
+ \cite{rei2017semi}, and currently serve as the state of the art machine learning methods, utilizing powerful contextual 
+ word embeddings in an unsupervised setting \cite{bell2019context}, overcoming the disadvantages of prior methods that 
+ require large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/active-learning.tex
updated related work

Active Learning has been widely studied in Natural Language Processing and often integrated as an effective approach in low resource scenaria in modern neural network systems and for a variety of tasks. 
\citet{lu2020investigating} suggest that representations generated from pre-trained transformer neural network models, are more effective in Active Learning for text classification, than using simpler word embeddings.

Closer to our Machine Translation objective, \citet{zhang2018active} propose two methods, for sentence selection based on considering semantic similarity between sentence embeddings or decoder probabilities as tokens of translation quality, while \citet{peris2020active} explore the application of active learning techniques in the interactive translation of large data streams. The latter work uses the attention mechanism of a neural machine translation system to query only for those sentences worthy of human annotation for translation.

In a more recent approach, \citet{zeng2019empirical} perform an empirical evaluation of different AL methods for Transformers \cite{vaswani2017attention}, analyzing data-driven approaches, that sample instances using two sets of labeled and unlabeled sentences, and model-driven methods, which additionally incorporate information from the current model into sampling. However their work notes the weak performance of Coverage Sampling compared to the other techniques, due to the complex nature of the state-of-the art multi-layer multi-head Natural Language Processing architectures, a phenomenon we are addressing with the current work.

A line of work has also explored the shortcomings of Active Learning approaches in Machine Translation. \citet{lowell2018practical} observe the performance drop issues arising across different models and tasks and discuss the methods' generalization constraints. Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a neural machine translation system in learning sentence semantic representations.

%Recent work in machine translation approaches has focused on integrating active learning
%with interaction-based neural machine translation. These modifications have been experimentally 
%employed with unbounded real-time streaming data \cite{peris2020active} with the objective of selecting 
%only those sentences which are very difficult for the translation system to accurately classify upon %
%during the initial stages. Results have shown promise in improving the overall quality of translation 
%and reducing human intervention in the process. A core component of this approach involves tweaking the 
%sampling strategies involved to maximize the probability of selecting only the most “difficult” sentences. 
%However, these results have a lack of representation and probable efficacy with respect to low-resource-based 
%multilingual paradigms. The effectiveness of slight alterations in the overall encoder-decoder transformer 
%network also needs to be experimented upon to possibly generate higher quality translations. s

### 2020-10-10 Paper/error-classification.tex
updated related work

--- 2020-10-10 Paper/error-classification.tex
@@
 In the former category, approaches focus on describing detailed error typologies to be used in conducting a systematic manual error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}.
-On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output of a MT system and its reference translation.
-Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous approaches to multi-label and multi-error automatic classification \cite{popovic2019automatic}.
+On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output sentence of a Machine Translation system and its reference translation.
+Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous works to multi-label and multi-error automatic classification \citet{popovic2019automatic}.
 
-In the most recent approaches, error detection is examined as an application of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}, and currently serve as the state of the art machine learning methods, utilizing powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, overcoming the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.
+In the most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}.
+The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/linguistic-representations.tex
updated related work

The work of \citet{belinkov2020linguistic} is a significant step in collecting and interpreting all approaches that examine the linguistic nature of the representations learned by modern complex neural network Machine Translation models, specifically LSTMs \citep{bahdanau2014neural}. The authors focus on three large categories of language properties, morphology, syntax and semantics, show that each category of information is better captured at a different layer of the architecture, and set the ground for further exploration of linguistic representations of more state-of-the-art models, such as the Transformer \citep{vaswani2017attention}.

### 2020-10-10 Paper/error-classification.tex

@@
 
-In the most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}.
+In most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}.
 The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/active-learning.tex
update related work

@@
-Active Learning has been widely studied in Natural Language Processing and often integrated as an effective approach in low resource scenaria in modern neural network systems and for a variety of tasks.
-\citet{lu2020investigating} suggest that representations generated from pre-trained transformer neural network models, are more effective in Active Learning for text classification, than using simpler word embeddings.
+Active Learning (AL) has been widely studied in Natural Language Processing and integrated in modern systems as an effective approach in low resource scenaria for a variety of tasks. 
+\citet{lu2020investigating} investigate AL in text classification, suggesting the effectiveness of representations generated from pre-trained Transformer models, compared to simple word embeddings.
 
-Closer to our Machine Translation objective, \citet{zhang2018active} propose two methods, for sentence selection based on considering semantic similarity between sentence embeddings or decoder probabilities as tokens of translation quality, while \citet{peris2020active} explore the application of active learning techniques in the interactive translation of large data streams.
-The latter work uses the attention mechanism of a neural machine translation system to query only for those sentences worthy of human annotation for translation.
+In NMT, \citet{zhang2018active} propose two methods for sentence selection, considering either the semantic similarity between sentence embeddings or the decoder probabilities as tokens of translation quality, while \citet{peris2020active} explore AL in the interactive translation of large data streams.
+The latter work uses an NMT attention mechanism to query only for those sentences worthy of human annotation for translation.
 
-In a more recent approach, \citet{zeng2019empirical} perform an empirical evaluation of different AL methods for Transformers \cite{vaswani2017attention}, analyzing data-driven approaches, that sample instances using two sets of labeled and unlabeled sentences, and model-driven methods, which additionally incorporate information from the current model into sampling.
-However their work notes the weak performance of Coverage Sampling compared to the other techniques, due to the complex nature of the state-of-the art multi-layer multi-head Natural Language Processing architectures, a phenomenon we are addressing with the current work.
+\citet{zeng2019empirical} perform an empirical evaluation of AL methods for Transformers, analyzing data- and model-driven sentences' sampling techniques.
+Their work notes the weak performance of Coverage Sampling, due to the complex nature of multi-layer multi-head architectures, an issue we are addressing with the current work.
 
-A line of work has also explored the shortcomings of Active Learning approaches in Machine Translation.
-\citet{lowell2018practical} observe the performance drop issues arising across different models and tasks and discuss the methods' generalization constraints.
-Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a neural machine translation system in learning sentence semantic representations.
+A line of work has also explored the shortcomings of AL approaches in NMT.
+\citet{lowell2018practical} observe performance drop issues arising across different models and tasks and discuss the methods' generalization constraints.
+Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a NMT system in learning sentence semantic representations.
 

### 2020-10-10 Paper/error-classification.tex
update related work

@@
-There exists a significant body of work in the area of error classification of text for machine translation, and proposed methods can be primarily divided into manual or automatic.
-In the former category, approaches focus on describing detailed error typologies to be used in conducting a systematic manual error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}.
-On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output sentence of a Machine Translation system and its reference translation.
-Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous works to multi-label and multi-error automatic classification \citet{popovic2019automatic}.
+There exists a significant body of work in the area of text error classification in MT, and proposed methods are primarily divided into manual or automatic.
+In the former category, approaches describe detailed error typologies to be used in conducting a systematic error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}.
+On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output sentence of a MT system and its reference translation.
+Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous works to multi-label and multi-error automatic classification \citep{popovic2019automatic}.
 
-In most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}.
-The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.
+Most recently, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}.
+The latest methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of older ones requiring large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/linguistic-representations.tex
update related work

@@
-The work of \citet{belinkov2020linguistic} is a significant step in collecting and interpreting all approaches that examine the linguistic nature of the representations learned by modern complex neural network Machine Translation models, specifically LSTMs \citep{bahdanau2014neural}.
-The authors focus on three large categories of language properties, morphology, syntax and semantics, show that each category of information is better captured at a different layer of the architecture, and set the ground for further exploration of linguistic representations of more state-of-the-art models, such as the Transformer \citep{vaswani2017attention}.
+The work of \citet{belinkov2020linguistic} is a significant step in presenting all approaches that examine the linguistic nature of the representations learned for MT in modern complex neural networks, specifically in LSTMs \citep{bahdanau2014neural}.
+The authors focus on three large categories of language properties, morphology, syntax and semantics, show that each type of information is better captured at a different layer of the architecture, and set the ground for further exploration of linguistic representations in MT with Transformer-based models \citep{vaswani2017attention}.

### 2020-10-11 Datasets/ContraWSD/score.sh
Added ContraWSD text dataset

@@ -1,0 +1,40 @@
+#!/bin/bash
+
+#######################################################
+#    Example script to use test sets for evaluation   #
+#######################################################
+
+# path to moses decoder: https://github.com/moses-smt/mosesdecoder
+mosesdecoder=path-to-mosesdecoder
+truecasemodel_dir=path-to-your-truecase-models
+
+# path to subword segmentation scripts: https://github.com/rsennrich/subword-nmt
+subword_nmt=path-to-subword-nmt
+bpemodel_dir=path-to-your-bpe-model
+
+# path to nematus: https://www.github.com/rsennrich/nematus
+nematus_dir=path-to-nematus
+nmt_model_dir=path-to-directory-containing-your-model
+nmt_model=path-to-your-model.npz
+
+wsd_dir=path-to-this-repo
+eval_dir=evaluation-directory
+target=en ## or fr
+testset=$wsd_dir/de-$target.final
+
+
+## prepare NMT_testsets
+python $wsd_dir/json_to_plaintext.py $testset $target
+
+#### pre-process test sets as required by your NMT model, e.g.
+cat $testset.de | $mosesdecoder/scripts/tokenizer/normalize-punctuation.perl -l de | $mosesdecoder/scripts/tokenizer/tokenizer.perl -l de | $mosesdecoder/scripts/recaser/truecase.perl -model $truecasemodel_dir/truecase-model.de | python $subword_nmt/apply_bpe.py --codes $bpemodel_dir/de$target.bpe > $testset.bpe.de
+cat $testset.$target | $mosesdecoder/scripts/tokenizer/normalize-punctuation.perl -l $target | $mosesdecoder/scripts/tokenizer/tokenizer.perl -l $target | $mosesdecoder/scripts/recaser/truecase.perl -model $truecasemodel_dir/truecase-model.$target | python $subword_nmt/apply_bpe.py --codes $nmt_model_dir/de$target.bpe > $testset.bpe.$target
+
+## score test set
+(cd $nmt_model_dir && THEANO_FLAGS=floatX=float32,device=cuda0,gpuarray.preallocate=0.8,on_unused_input=warn python $nematus_dir/nematus/score.py -m $nmt_model -s $testset.bpe.de -t $testset.bpe.$target -o $eval_dir/nmt.scores.$target -n -b 20)
+
+cat $eval_dir/nmt.scores.$target | python -c "import sys 
+for line in sys.stdin:
[…]

### 2020-10-11 Datasets/ContraWSD/testsuite_wmt18/evaluate.py

@@ -1,0 +1,478 @@
+#!/usr/bin/python3
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function, unicode_literals
+import sys
+reload(sys);
+sys.setdefaultencoding("utf8")
+import json
+import argparse
+from collections import defaultdict, OrderedDict
+from operator import gt, lt
+import scipy
+import scipy.stats
+import re
+
+
+FREQUENCY_BINS = OrderedDict()
+# value for higher frequencies
+FREQUENCY_BINS[">10k"] = []
+DEFAULT_FREQUENCY = ">10k"
+FREQUENCY_BINS[">5k"] = range(5001, 10001)
+FREQUENCY_BINS[">2k"] = range(2001, 5001)
+FREQUENCY_BINS[">1k"] = range(1001, 2001)
+FREQUENCY_BINS[">500"] = range(501,1001)
+FREQUENCY_BINS[">200"] = range(201,501)
+FREQUENCY_BINS[">100"] = range(101,201)
+FREQUENCY_BINS[">50"] = range(51,101)
+FREQUENCY_BINS[">20"] = range(21,51)
+FREQUENCY_BINS["0-20"] = range(0,21)
+
+
+FREQUENCY_TO_BIN = {}
+for key in FREQUENCY_BINS:
+    for freq in FREQUENCY_BINS[key]:
+        FREQUENCY_TO_BIN[freq] = key
+
+            
+testwords = {
+ 'Absatz': ['heel' , 'paragraph' , 'sales' ],
+ 'Abzug': ['discount|subtraction|deduction' , 'disengagement|decampment|departure|withdrawal' , 'trigger' ],
+ 'Anlage|Anlagen': ['attachment|attachments|annex|annexes' , 'installation|unit|construction|facility|installations|units|constructions|facilities|plant' , 'investment|investments' ],
+ 'Annahme': ['adoption|approval|acceptance|acceptation|acception' , 'assumption|hypothesis|guess|conjecture|presumption' ],
+ 'Art': ['manner|mode|kind|style' , 'species|breed' ],
+ 'Aufgabe': ['abandonment|surrender' , 'task|assignment|commission|exercise' ],
+ 'Auflösung': ['dissolution|termination|liquidation|solution|cancellation|cancelation|disintegration|disbandment|breakup|break-up|dispersal|dismantling' , 'resolution' ],
[…]

### 2020-10-11 Datasets/ContraWSD/testsuite_wmt18/final_eval.py

@@ -1,0 +1,197 @@
+#!/usr/bin/python3
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function, unicode_literals
+import sys
+reload(sys);
+sys.setdefaultencoding("utf8")
+import json
+import argparse
+from collections import defaultdict, OrderedDict
+from operator import gt, lt
+import scipy
+import scipy.stats
+import re
+
+FREQUENCY_BINS = OrderedDict()
+# value for higher frequencies
+FREQUENCY_BINS[">10k"] = []
+DEFAULT_FREQUENCY = ">10k"
+FREQUENCY_BINS[">5k"] = range(5001, 10001)
+FREQUENCY_BINS[">2k"] = range(2001, 5001)
+FREQUENCY_BINS[">1k"] = range(1001, 2001)
+FREQUENCY_BINS[">500"] = range(501,1001)
+FREQUENCY_BINS[">200"] = range(201,501)
+FREQUENCY_BINS[">100"] = range(101,201)
+FREQUENCY_BINS[">50"] = range(51,101)
+FREQUENCY_BINS[">20"] = range(21,51)
+FREQUENCY_BINS["0-20"] = range(0,21)
+
+
+FREQUENCY_TO_BIN = {}
+for key in FREQUENCY_BINS:
+    for freq in FREQUENCY_BINS[key]:
+        FREQUENCY_TO_BIN[freq] = key
+
+def finalize(automatic_eval, manual_eval, verbose=False, ignore_wmt=False):
+    results = json.load(automatic_eval)
+    manual_results = json.load(manual_eval)
+
+    
+    ## correct number of only_correct from automatic evaluation + correct==1 from manual evalutation
+    automatic_correct =0
+    automatic_other = 0
+    automatic_both = 0
+    automatic_none = 0
+    automatic_unfound_in_correct =0
+    
+    for category in results['by_category']:
+        
+        only_correct_found = results['by_category'][category]['only_correct']
+        only_other = results['by_category'][category]['only_other']
+        found_both = results['by_category'][category]['found_both']
+        results['by_category'][category]['correct'] = only_correct_found
+        ## set unfound for all categories and frequencies
+        if 'unfound' not in results['by_category'][category]:
+            results['by_category'][category]['unfound'] =0
+        if 'unfound_in_correct' not in results['by_category'][category]:
+            results['by_category'][category]['unfound_in_correct'] =0    
+            
+        unfound = results['by_category'][category]['unfound']
[…]

### 2020-10-11 Scripts/FCE_Parser/FCECorpusHandler.py
small update

@@ -222,12 +222,18 @@ class FCECorpusHandler:
                 print()
                 print(f)
             mydoc = minidom.parse(fce_dir_dataset + f)
-            items_essay = mydoc.getElementsByTagName('p')
-            for item_essay in items_essay:
-                incorrect_sent, correct_sent, error_sent = self.strip_str(
-                    item_essay, verbose=verbose)
-                incorrect_sentences.append(incorrect_sent)
-                correct_sentences.append(correct_sent)
-                error_tags.append(error_sent)
+            # fetch each answer in doc
+            answer = mydoc.getElementsByTagName('coded_answer')
+            # items_essay = mydoc.getElementsByTagName('p')
+
+            # loop through every answer/essay
+            for ans in answer: 
+                items_essay = ans.getElementsByTagName('p')
+                for item_essay in items_essay:
+                    incorrect_sent, correct_sent, error_sent = self.strip_str(
+                        item_essay, verbose=verbose)
+                    incorrect_sentences.append(incorrect_sent)
+                    correct_sentences.append(correct_sent)
+                    error_tags.append(error_sent)
         
         print(error_tags)

### 2020-10-12 Scripts/FCE_Parser/FCECorpusHandler.py
updated parser

@@ -8,6 +8,8 @@ import tarfile
 from collections import defaultdict
 import shutil
 import glob
+from bs4 import BeautifulSoup
+import csv
 
 __author__ = "Gwena Cunha"
 
@@ -152,22 +154,35 @@ class FCECorpusHandler:
         incorrect_sent = ''
         correct_sent = ''
         error_tags = ''
+        errors = []
+        pos = 0
         for child in item_essay.childNodes:
             if child.localName is None:  # no child nodes
                 segment = child.data
                 incorrect_sent += segment
                 correct_sent += segment
+
+                # increment pos 
+                pos += len(segment)
                 # print(segment)
             else:  # 'NS', 'i', 'c'
                 inc_sent, cor_sent = self.recursive_NS_tag_strip(child)
-                if child._attrs is not None:
-                    error_tags += child._attrs['type'].value + ","
                 incorrect_sent += inc_sent
                 correct_sent += cor_sent
+                if child._attrs is not None:
+                    # to get incorrect word, incorrect_sent[errors[err_no]["start_off"]: errors[err_no]["end_off"]]
+                    errors.append({"tag": child._attrs['type'].value, "incorrect": inc_sent, "correct": cor_sent, "start_off": pos, 
+                    "end_off": pos + len(inc_sent)})
+                else: 
+                    print("No Error tag!; In-Correct:", inc_sent, "Correct:", cor_sent)    
+
+                # update pos
+                pos += len(inc_sent)
+
         if verbose:
             print("Incorrect sentence: " + incorrect_sent)
             print("Correct sentence: " + correct_sent)
-        return incorrect_sent, correct_sent, error_tags
+        return incorrect_sent, correct_sent, errors
 
     def recursive_NS_tag_strip(self, item_ns):
         incorrect_sent = ''
@@ -212,10 +227,7 @@ class FCECorpusHandler:
         train_dev_test_files = [f for f in os.listdir(
             fce_dir_dataset) if f.endswith('.xml')]
 
-        # convert xml to txt
-        incorrect_sentences = []
-        correct_sentences = []
-        error_tags = []
+        fields = ["incorrect", "correct", "error"]
 
         for f in train_dev_test_files:
             if verbose:
@@ -227,13 +239,49 @@ class FCECorpusHandler:
             # items_essay = mydoc.getElementsByTagName('p')
 
             # loop through every answer/essay
+            ans_count = 0
             for ans in answer: 
+                # convert xml to txt
[…]

### 2020-10-12 Scripts/CONLL14_Parser/parser.py
added conll parser file

@@ -1,0 +1,50 @@
+import re
+import os
+import glob
+import pprint
+from bs4 import BeautifulSoup
+import csv
+import pandas as pd
+from xml.dom import minidom
+import urllib.request
+import zipfile
+import tarfile
+from collections import defaultdict
+import shutil
+
+documents = []
+for file in glob.glob("*.sgml"):
+    with open(file,'r') as f:
+        sgml = f.read()
+        soup = BeautifulSoup(sgml,'lxml')
+        # want - mistake, type, correction
+        # filter first by doc. Save each doc in a object
+        # for each doc, filter by paras and mistakes
+        docs = soup.find_all('doc')
+        for d in docs:
+            paras = d.find_all('p')
+            mistakes = d.find_all('mistake')
+            # doc = {"paras": paras,"mistakes":mistakes}
+            # documents.append(doc)
+            for mistake in mistakes:
+                # print("hi")
+                # Fetching Error types and Corrections
+                types = mistake.type.text.split("\n")
+                corrections = mistake.correction.text.split("\n")
+                # Fetching offsets for mistaken-words
+                start_para = int(mistake.attrs["start_par"])
+                end_para = int(mistake.attrs["end_par"])
+                start_off = int(mistake.attrs["start_off"])
+                end_off = int(mistake.attrs["end_off"])
+
+                if start_para != end_para:
+                    #print("unhandled case")
+                    break
+                # get word using offset
+                word_text = paras[start_para-1].text
+                word = word_text[start_off:end_off+1]
+                #print(word)
+                documents.append({'Paragraphs':str(paras[start_para-1]),'Start Offset':start_off, 'End Offset':end_off, 'Mistake-Words':str(word),'Error Type':str(types),'Corrections':str(corrections)})
+              
+df = pd.DataFrame(documents)
+csv_data = df.to_csv(index=False)

### 2020-10-12 Scripts/CONLL14_Parser/parser.py
updates to conll parser

@@ -12,8 +12,9 @@ import tarfile
 from collections import defaultdict
 import shutil
 
+
 documents = []
-for file in glob.glob("*.sgml"):
+for file in glob.glob("Scripts/CONLL14_Parser/data/*.sgml"):
     with open(file,'r') as f:
         sgml = f.read()
         soup = BeautifulSoup(sgml,'lxml')
@@ -24,27 +25,48 @@ for file in glob.glob("*.sgml"):
         for d in docs:
             paras = d.find_all('p')
             mistakes = d.find_all('mistake')
-            # doc = {"paras": paras,"mistakes":mistakes}
-            # documents.append(doc)
+
+            temp = []
+            original = [para.text for para in paras]
+            texts = [para.text for para in paras]
+            
+            mistake_counter = 0
             for mistake in mistakes:
-                # print("hi")
+                
                 # Fetching Error types and Corrections
-                types = mistake.type.text.split("\n")
-                corrections = mistake.correction.text.split("\n")
+                # types = mistake.type.text.split("\n")
+                tag = mistake.find_all('type')[0].text
+                # corrections = mistake.correction.text.split("\n")
+                correction = mistake.find_all('correction')[0].text
                 # Fetching offsets for mistaken-words
                 start_para = int(mistake.attrs["start_par"])
                 end_para = int(mistake.attrs["end_par"])
-                start_off = int(mistake.attrs["start_off"])
+                start_off = int(mistake.attrs["start_off"]) 
                 end_off = int(mistake.attrs["end_off"])
 
                 if start_para != end_para:
                     #print("unhandled case")
                     break
                 # get word using offset
-                word_text = paras[start_para-1].text
+                # special case
+                word_text = original[start_para-1]
                 word = word_text[start_off:end_off+1]
+                
+                # replace word in text 
+                word_text = word_text[:start_off] + " " + correction + " " + word_text[start_off+ len(correction):]
+                texts[start_para - 1] = word_text
+                
+                temp.append({"para":start_para - 1, "stuff": {"tag": tag, "start_off": start_off, "end_off": end_off, "correct": correction, "incorrect": word}})
+            
+            output = []
+            for t in temp: 
+                para_id = t["para"]
+                output.append({"incorrect": original[para_id], "correct": texts[para_id], "error": t["stuff"]})
+
+            print(output)
+
                 #print(word)
[…]

### 2020-11-12 Paper/workflow.tex
added new files for paper

\subsection{Error Classification}
\label{sec:method-error}

    \subsubsection{Datasets}
    \input{datasets.tex}
    \label{sec:method-error-datasets}

    \subsubsection{Data Processing}
    \input{data-processing.tex}
    \label{sec:method-error-dataprocessing}

    \subsubsection{Classifier}
    \input{error-classifier.tex}
    \label{sec:method-error-errorclassifier}

### 2020-11-12 Paper/workflow.tex
added basic info on error classification

@@
 \label{sec:method-error}
+The following section outlines the error classification process for identifying errors 
+in the machine translated outputs from German/Gujarati to English. Specifically, we are 
+interested in the three main error types: 
+    (1) Grammar: mis-selection and mis-ordering errors including contraction, verbs, 
+                agreement; 
+    (2) Lexis: errors like omission of words, addition of extra words (that are not needed), 
+                and un-translated outputs; and 
+    (3) Orthography: errors that deal with punctuation, improper capitalization, spelling 
+                mistakes, etc. 
+Additionally, we also attempted at classification of semantic errors (wrong choice, collocational errors and idoms)
+and discourse errors (style, variety, etc.).
 

### 2020-11-12 Paper/datasets.tex
added fce dataset info

To train our classifier on the target language (English), we explored three
different datasets, namely: (1) Cambridge FCE Corpus; (2) CoNLL-14; (3) CoNLL-15

\paragraph{Cambridge FCE Corpus.}
The Cambridge First Certificate Exam Learner Corpus is a 16-million word 
corpus of English examination scripts collected by Cambridge University Press. 
The scripts categorize errors in the sentences into approximately 80 error labels, 
along with corrections \cite{NichollsFce}.

\paragraph{CoNLL-13.}

\paragraph{CoNLL-14.}

### 2020-11-13 Paper/data-processing.tex
more updates on the paper for error classification

We divided data processing into \emph{x} steps -
    (1) Mapping different error labels to five main error labels;
    (2) Combining the dataset with both correct and incorrect sentences; 
    (3) Encoding error labels and building an error vector;
    (4) Ensuring sentence "uniqueness"; and

\subparagraph{Mapping Error Labels.}
The approximately 80 different error labels were mapped to the their five higher 
levels manually. \cite{NichollsFce} describes the tagging process for the error labels, 
where tags starting with "F" indicated incorrect form, "M" indicated missing, "R" indicated replacing,
"U" undicated unnecessary, etc. Further, the taxonomy of translation errors from \cite{costaTaxonomyErrorLabels}
was used for the appropriate mappings.

\subparagraph{Combining dataset with correct and incorrect sentences.}
The FCE text corpus provides the examination scripts in an XML format. These are initially converted to "txt" files, 
and then parsed into a comma separated format (csv) with every sentence/group of sentences with their error tags. 
In case of multiple errors per sample, the sentence/group is repeated for every tag in the csv file. 
Since the Cambridge FCE corpus provided us with error tags for sentences along with their 
corrections, the correct sentences are filtered out separately. Further, an additional "CO" label denoting correctness
is attached to each of these sentences and then are appended to the dataset containing incorrect ones.

\subparagraph{Encoding Error Labels \& Error vector.}
Classifying sentences grouped into six categories (5 error labels and 1 correct label) looks to be a multi-class 
classification problem, however, it is possible that a given sentence or group of sentences might have multiple errors 
in them. Thus, every sample's error tag is one-hot-encoded: six new columns are added, each for a given error tag, with 
a "1" on the actual error tag's column. An error vector is built using these one-hot-encodings, each vector for a given sample 
of length equalling 6. As sentences can have multiple errors, those samples with repeating rows are grouped, and their 
error vectors are aggregated.

\subparagraph{Sentence Uniqueness.}
Further, it is possible to have a sentence that is correct in one context, but has errors in 
another context (a simple example would be closing statements). For this reason, those samples that have a "1" for both "CO" and 
other error labels are dropped from the dataset.

### 2020-11-13 Paper/data-processing.tex
small update

@@
     (2) Combining the dataset with both correct and incorrect sentences; 
-    (3) Encoding error labels and building an error vector;
-    (4) Ensuring sentence "uniqueness"; and
+    (3) Encoding error labels and building an error vector; and
+    (4) Ensuring sentence "uniqueness";
 
